%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%W  install.tex           POLENTA documentation            Bjoern Assmann
%W                                                     
%W                                                     
%W                                                       
%%
%H  @(#)$Id$
%%
%Y 2003
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Chapter{Installation}

\atindex{Installation}{@Installation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Section{Installing this package}\null

The Guarana package is part of the standard distribution of {\GAP} and
so normally there should be no need to install it separately.
If by any chance it is not part of your {\GAP} distribution, then 
the standard method is to unpack	 the package into the `pkg'
directory  of your {\GAP} distribution.  This will create a `guarana'
subdirectory. 
For other non-standard options please see  Chapter~"ref:Installing a
GAP Package" of the {\GAP} Reference Manual.

Note that the GAP-Packages Polycyclic and Polenta
are needed for this package.
Normally they should be contained in your distribution. If not, 
they can be obtained at
\begintt
               www.gap-system.org/Packages/packages.html             

\endtt


%To create the documentation, go into the `doc' directory and type
%`make_doc'.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Section{Loading the Guarana package}\null

\atindex{Loading the Guarana package}{@loading the {\Guarana} package}
If the {\Guarana} Package is not already loaded 
then you have to request it explicitly. 
This  can be 
done by `LoadPackage("guarana")'.
The `LoadPackage' command is described in Section~"ref:LoadPackage"
in the {\GAP} Reference Manual.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Section{Running the test suite}

    Once the package is installed, it is possible to check the correct
    installation by running the test suite of the package.

\beginexample
    gap> Read( "mygap/pkg/guarana/tst/testall.g" );
\endexample
    where `mygap' needs to be replaced with the directory where {\GAP}
    was installed. For more details on  Test Files see 
    Section~"ref:Test Files" of the 
    {\GAP} Reference Manual.

    If the test suite runs into an error, 
    then please send a message
    to `bjoern@mcs.st-and.ac.uk' including the error message.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%E


